### 2021-06-11 paper/report.tex
Add references to mental health outcomes.

The reason lies in the fact that a substantial share of these tests is driven by an
elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or following
up on a positive test of a household member. The latter is essentially a form of contact
tracing, which has been shown to be very effective \citep{Contreras2021,
Kretzschmar2020}. This is also the reason for why the number of tests performed fall at
the very end of our study period. Falling infection rates mean that there are fewer
events triggering private test demand.\comment[id=HM]{Positive rates along the three
channels might be nice here, if previous comment is not a quant
story}\comment[id=K]{Working on it}\comment[id=HM]{I think there is a story in here about
risk conditional on past exposure vs. prospective risk in gatherings, but it is too late
to work through it. We might just want to calculate the
probabilities.}\comment[id=K]{Yes, we have both in the private reasons. Retrospective
after a case in the household and prospective in anticipation of participation in a
weekly meeting with friends. However, we cannot easily turn these separately on and off
at the moment as they use the same multiplier. We could do, however, do this in the
future.}

Two of the most contentious NPIs concern schools and mandates to work from home. In many
countries, schools switched to remote instruction during the first wave, so did Germany.
After the summer break, they were operating at full capacity with increased hygiene
measures, before being closed again from mid-December on. Some states started opening
them gradually in late February, but usual operation was not back until the beginning of
June. Figure~\ref{fig:school_scenarios} shows the effects of different policies regarding
school starting at Easter, at which point rapid tests had become widely available. We
estimate the realized scenario to have essentially the same effect as a situation with
closed schools. Under fully opened schools with mandatory tests, total infections would
have been 7\% higher; this number rises to 20\% without tests. These effect sizes are
broadly in line with empirical studies, e.g., \citet{Vlachos2021}\comment[id=HM]{Need a
back-of the envelope calculation} To use another metric, the effective weekly
reproduction number differs by $0.017$ and $0.045$, respectively. In light of the large
negative effects school closures have on children and parents\comment[id=HM]{need to cite
a couple of poor learning outcomes / mental health papers. There must be well-published
ones}---and in particular on those with low socio-economic status---these results in
conjunction with hindsight bias suggest that opening schools combined with a testing
strategy would have been beneficial. In other situations, and particular when no test
strategy is available, trade-offs may well be different.

>>>>

The reason lies in the fact that a substantial share of these tests is driven by an
elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or following
up on a positive test of a household member. The latter is essentially a form of contact
tracing, which has been shown to be very effective \citep{Contreras2021,
Kretzschmar2020}. This is also the reason for why the number of tests performed fall at
the very end of our study period. Falling infection rates mean that there are fewer
events triggering private test demand.\comment[id=HM]{Positive rates along the three
channels might be nice here, if previous comment is not a quant
story}\comment[id=K]{Working on it}\comment[id=HM]{I think there is a story in here about
risk conditional on past exposure vs. prospective risk in gatherings, but it is too late
to work through it. We might just want to calculate the
probabilities.}\comment[id=K]{Yes, we have both in the private reasons. Retrospective
after a case in the household and prospective in anticipation of participation in a
weekly meeting with friends. However, we cannot easily turn these separately on and off
at the moment as they use the same multiplier. We could, however, do this in the
future.}

Two of the most contentious NPIs concern schools and mandates to work from home. In many
countries, schools switched to remote instruction during the first wave, so did Germany.
After the summer break, they were operating at full capacity with increased hygiene
measures, before being closed again from mid-December on. Some states started opening
them gradually in late February, but usual operation was not back until the beginning of
June. Figure~\ref{fig:school_scenarios} shows the effects of different policies regarding
school starting at Easter, at which point rapid tests had become widely available. We
estimate the realized scenario to have essentially the same effect as a situation with
closed schools. Under fully opened schools with mandatory tests, total infections would
have been 7\% higher; this number rises to 20\% without tests. These effect sizes are
broadly in line with empirical studies, e.g., \citet{Vlachos2021}\comment[id=HM]{Need a
back-of the envelope calculation} To use another metric, the effective weekly
reproduction number differs by $0.017$ and $0.045$, respectively. In light of the large
negative effects school closures have on children and parents \citep(Luijten2021,
Melegari2021) \comment[id=HM]{need to cite a couple of poor learning outcomes / mental
health papers. There must be well-published ones}\comment[id=K]{I googled and found two
that I think are at least not terrible but I also didn't find anything really well
published}---and in particular on those with low socio-economic status---these results in
conjunction with hindsight bias suggest that opening schools combined with a testing
strategy would have been beneficial. In other situations, and particular when no test
strategy is available, trade-offs may well be different.
